---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Omero Catan"
date: "September 6, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## CO2 Dataset

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

The CO2 r dataset was used for the application and presentation.

## Carbon Dioxide Uptake in Grass Plants

### **Source**
Potvin, C., Lechowicz, M. J. and Tardif, S. (1990) “The statistical analysis of ecophysiological response curves obtained from experiments involving repeated measures”, Ecology, 71, 1389–1400.
Pinheiro, J. C. and Bates, D. M. (2000) Mixed-effects Models in S and S-PLUS, Springer.

The data frame has 84 rows and 5 columns of data from an experiment on the coold tolerance of the grass species Enchinochloa crus-galli.

## Variables

### **Variables**
- Plant: An ordered Factor with levels Qn1 < Qn2 < Qn3<…..<Mc1 giving a unique     identifier for each plant.
- Type: A factor with levels Quebec Mississippi giving the origin of the plant.
- Treatment: A factor with levels nonchilled, chilled.
- conc: A numeric vector of ambient carbon dioxide concentrations (mL/L).
- uptake: A numeric vector of carbon dioxide uptake rates (umol/m^2 sec).

## Application Calculation
My application uses the CO2 dataset in R and based on the user input of a variable from the drop-down list, calculates boxplots comparing the selected variable to the CO2 uptake levels.

### **Top of Dataset**
```{r}
head(CO2)
```